% Joseph Silas Tippens' Resume
% URL: https://github.com/Poeticode/Resume
% Forked from James Pearson Hughes' resume
% URL: https://github.com/xiongchiamiov/Resume
% Which was forked from Chris Gibson's resume
% URL: https://github.com/cgibson/Resume
% Which is in turn based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}

\name{\huge \sc{Joseph Silas Tippens}\vspace{2mm}}
{
    \hfill me@silentsilas.com       \vspace{0mm}\\\vspace{0mm}%
    \hfill https://silentsilas.com           \vspace{0mm}\\\vspace{0mm}%
    \hfill https://github.com/Poeticode \vspace{0mm}\\\vspace{-9mm}%
}

\begin{resume}

    \vspace{-3mm}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    \textbf{\textsl{Interactive Developer}} with a penchant for \textbf{performance}, \textbf{novelty}, and \textbf{security}. Obsessed with human language and the impact of emergent technologies on society. 

    \vspace{-1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL} \large{E}\small{XPERIENCE}}}

    \textbf{\listing L2D} \textsl{(formerly Level2d)} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Interactive Developer} \hfill \textbf{December 2013 -- present}\\
    Began an internship to learn modern front-end development, which evolved into a full-time position.\\
    Developed several websites utlizing a wide-range of technologies, including modern build tools (Grunt / Gulp, Webpack, SCSS), Vue, Git, Foundation, and ThreeJS.\\
    Experimented with visualizing realtime Kinect data in the browser, via NodeJS Websockets, LZMA compression, ThreeJS, and a custom Python solution. \\
    Implemented an API for a media player progressive web application using Elixir (Phoenix Framework) and AWS (S3, Cloudfront, RDS). \\
    Developed several mixed reality experiences using the Unreal Engine and Unity3D, one of which is deployed to the Steam Store (Spare Teeth VR). \\
    Introduced several good-hygiene security habits at the organizational level.

\sectionline

    %__________________________________________________________________________________________________________________
    % Passion Projects
    \section{\mysidestyle \textbf{\large{P}\small{ASSION} \large{P}\small{ROJECTS}}}

    \textbf{\listing Silent Silas}\\
    \textsl{https://github.com/Poeticode/silentsilas.com} \hfill \textbf{July 2018 -- present}\\
    A performant, static portfolio/blog site showcasing poetry and side-projects.\\
    Generated with Hugo, which is then deployed to IPFS and a personal Apache server.\\
    Written in HTML, SCSS, and ES6 Javascript, with various ThreeJS visualizations.\\
    Gathers analytics via a self-hosted, GDPR-compliant FOSS service (Matamo).\\
    Uses a self-hosted, GDPR-compliant FOSS commenting system (Commento) for each post. 

    \textbf{\listing Chattanooga Poets Collective}\\
    \textsl{https://github.com/Poeticode/hub} \hfill \textbf{June 2019 -- present}\\
    Volunteered to build out and host a site where attendees to our monthly poetry meetings could freely upload their works and comment on others. The frontend is built with ES6 and styled with Tachyons, with a Phoenix backend to handle authentication, profile information, and file uploading. \\
    Accessible at https://chattanoogapoetscollective.com/

    \textbf{\listing OuREM}\\
    \textsl{https://github.com/Poeticode/OuREM} \hfill \textbf{October 2018 -- present}\\
    A cross-platform mobile application that interfaces with the Oura Ring. It allows the user to quickly add an entry to their dream journal via text-to-speech technologies, and visualizes your past REM cycles with tag clouds of their accompanying dream entry.\\
    Written in Dart with the Flutter framework.

    \textbf{\listing Pr1vy}\\
    \textsl{https://github.com/Poeticode/Privy} \hfill \textbf{February 2019 -- present}\\
    An open-source and cross-platform mobile application to interactively show the math and magic behind password security, encrypted communications, and data integrity verification. Written in Vue and Typescript, designed with the Quasar framework, and deployed via Cordova.

    \vspace{-1mm}

\sectionline


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing Covenant College}, Lookout Mountain, Georgia \vspace{1mm}\\
    \textsl{B.S of Computer Science with a Cyber Security Concentration} \hfill \textbf{August 2011 -- May 2015}\vspace{-3mm}\\\vspace{-1mm}%

    \vspace{-1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Skills / Keywords
    \section{\mysidestyle \textbf{\large{S}\small{KILLS} / \large{K}\small{EYWORDS}}}

    \textbf{Linux:} CentOS, Ubuntu / Debian\\
    \textbf{Scripting:} Bash, Python, Ruby\\
    \textbf{Backend:} PHP (CraftCMS, Laravel, custom), Elixir (Phoenix), NodeJS (Express)\\
    \textbf{Frontend:} HTML, CSS/SCSS, Javascript (ES6, Typescript, Vue, React, React Native, Webpack, ThreeJS), Dart (Flutter)\\
    \textbf{Databases:} MySQL, PostgreSQL\\
    \textbf{Web Application servers/proxies:} Apache, Nginx\\
    \textbf{Version control systems:} Git\\
    \textbf{Misc:} Amazon Web Services (S3, CloudFront, RDS), Docker, Ansible, Vagrant



\end{resume}
\end{document}
